Irt plot extra

### 2022-11-22 manuscript_v2.Rmd
added missing attention check items as bullet points

As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Participants were further asked to confirm that they participated in the survey for the first time. Additionally, five attention check items (e.g., "We want to make sure you are paying attention. What is 4+5?") were included among the questionnaires to ensure high data quality. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

>>>>

As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Participants were further asked to confirm that they participated in the survey for the first time.  All questions incorporating retrospective recall were aligned to a "past four weeks" period. Additionally, four attention check items  were included among the questionnaires to ensure high data quality, with the following phrasing:
- We want to make sure you are paying attention. What is 4+5?
- [...] Please select "Strongly disagree" here.
- [...] Please type in "nineteen" as a number.
- [...] Please select "Does not apply/I don't know." here.
